Place of death in NRS COVID-19 deaths: data processing for analysis, 2022 data

### 2022-02-11 covid_nrs_place_of_death_data_2022.Rmd
I have a strange feeling I've pushed this file before...

@@

total_deaths_overall <-
  merged_deaths_overall %>%
  compute_total_deaths_in_year() %>%
  left_join(historical_annual_average_overall, by = c("place_of_death")) %>%
  compute_ratio_of_annual_deaths_to_historical

>>>>

## helper function to remove rows of data where the historic period is inappropriate
remove_invalid_historic_period_for_year <- function(data_tbl) {
  data_tbl %>%
    filter(!(historic_period == "2016-2019, 2021" & year < 2022))
}

total_deaths_overall <-
  merged_deaths_overall %>%
  compute_total_deaths_in_year() %>%
  left_join(historical_annual_average_overall, by = c("place_of_death")) %>%
  compute_ratio_of_annual_deaths_to_historical %>%
  remove_invalid_historic_period_for_year()

@@
